Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-08-02 paper/paper.tex
abstract

\begin{document}
% \captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Fig.}}
% \history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
% \doi{10.1109/ACCESS.2017.DOI}

% \title{Preparation of Papers for IEEE ACCESS}
% \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
% \uppercase{Second B. Author\authorrefmark{2}, and Third C. Author,
% Jr}.\authorrefmark{3},
% \IEEEmembership{Member, IEEE}}
% \address[1]{National Institute of Standards and 
% Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
% \address[2]{Department of Physics, Colorado State University, Fort Collins, 
% CO 80523 USA (e-mail: author@lamar.colostate.edu)}
% \address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
% 80309 USA}
% \tfootnote{This paragraph of the first footnote will contain support 
% information, including sponsor and financial support acknowledgment. For 
% example, ``This work was supported in part by the U.S. Department of 
% Commerce under Grant BS123456.''}

@@

% \begin{abstract}

% \end{abstract}

% \begin{keywords}
% Enter key words or phrases in alphabetical 
% order, separated by commas. For a list of suggested keywords, send a blank 
% e-mail to keywords@ieee.org or visit \underline
% {http://www.ieee.org/organizations/pubs/ani\_prod/keywrd98.txt}
% \end{keywords}

% \titlepgskip=-15pt

% \maketitle

\section{Introduction}
% unmanned vvehcile
\PARstart{I}{n} recent years, the unmanned vehicle (UV) has attracted attention due to the advances in communication technology, sensing devices, and computing power. It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans. Due to these benefits, it has been widely used in many scenarios, such as search and rescue, battlefield, logistics and transportation, and surveillance, etc (cite:UV). Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}. However, the cost is that the design of such a multi-agent system becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, task allocation, and cooperation between agents. In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued (cite:HMAS). Compared with homogeneous multi-agent system, it can adapt to a wider variety of application scenarios. Although there are many types of UVs to make up such a system, Unmanned Aerial Vehicle (UAV) and Unmanned Ground Vehicle (UGV) have been the subject of major recent research because of their availability and applicability (cite:UAV-UGV). Additionally, the complementarity between them also makes such a system more potential. In other words, UAV is widely used in reconnaissance due to the high mobility. However, the carrying capacity of UAV is very low compared to UGV since there is no ground support. In contrast, UGV has higher carrying capacity but is easily restricted by ground obstacles and cannot move at high speed. For these reasons, a hybrid UAVs-UGVs team system will be more appealing.

To construct an unmanned HMAS, the three key capabilities are perception, decision-making and control. Perception is to obtain information through the sensor (e.g., localization or computer vision), decision-making is to make decisions through the sensor information, and control is to execute the decision-making content through the actuator. To limit the scope of this paper, we focus on decision-making and control only. The three main problem of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance. Task allocation is to optimally assign tasks to each agent, subject to constraints such as agent capabilities, fuel cost, time cost, etc \cite{9476736}. Path planning is to optimally plan paths to each agent, subject to constraints such as agent kinodynamic properties, distance, obstacles collision, etc (cite: path planning). Collision avoidance is to avoid collision with obstacles. Although collision avoidance is often concerned in path planning part, the collision avoidance system is also independently studied because of the requirements for the safety and reliability of the actual system \cite{9108245}.

To discuss an unmanned HMAS more concretely, we consider an UAVs-UGVs team system for search and rescue. For the need for search mobility, we choose quadrotor aircraft as UAV. In order to deal with the complex terrain of the search and rescue environment, biped robot was chosen as the UGV. Although other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system.

To the best of the authors' knowledge, most of the literature focus on only one specific problem, and few literatures illustrate the relationship between these problems for an unmanned HMAS. This leads us to propose an system architecture of UAV-robot team system (URTS) for search and rescue usage. The flowchart of decision-making and control process of URTS is also given. We divide it into five main hierarchical blocks, i.e., tack allocation, path planning, behavior layer, local motion planning and tracking control. It is because the UTRS needs to be able to assign different tasks to agents to perform first. After a task is assigned, if the task is to reach a target location, a path needs to be planned to reach it. To make agent move on the path, a behavior corresponding to the environment needs to be determined. Then, a local motion corresponding to the behavior of the agent needs to be planned. Finally, a controller must be designed to track the trajectory of the motion. In order to further limit the scope of the study, we will focus on the latter two blocks. But to illustrate how the whole system works, the first three problems are also briefly stated.

% To discuss the local motion planning problem and tracking control problem, the real mechanical system for each agent corresponds must be considered. To meet the need for search mobility, we choose quadrotor aircraft as UAV. The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control). In order to deal with the complex terrain of the search and rescue environment, biped robot was chosen as the UGV. Although other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system. However, to let the biped robot moving, not only the control problem (cite: robot control) but also the local motion planning problem need to be solved. The local motion planning of the walking of biped robot, i.e., stable walking parttern generation, is discussed in this paper. Related researches can be found in (cite: walking parttern).

The local motion planning is the bridge between path planning and tracking control since the path found by path planning algorithm and the path enforced to follow by a controller are not necessarily the same. The reason is that path planning algorithm usually treats the agent as a point, while the actual agent is a mechanical system for the tracking control design. A mechanical system means that there exist kinodynamic constraints. It makes certain paths impossible to follow for an agent, such as paths that are not smooth, have too large curvature, or require too large velocity and acceleration. Although there are some literatures tackle the path planning with the kinodynamic constraints of an actual mechanical system \cite{9384209}, this paper splits the step of path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity. Through this decomposition, we can focus on the local motion design of specific behaviors. The motion planning of flying behavior for UAV and walking behavior for robot is studied in this paper, especially the latter. Due to the challenge of the local motion planning of the walking of biped robot, i.e., stable walking parttern generation, it is a popular research topic (cite: walking parttern).

The tracking control is to control an agent to follow a desired trajectory. There are many control strategy for MAS. According to the way of the design of controller, it can be divided into centralized control and decentralized control in control field \cite{8931370}. Centralized control means there exist a powerful central controller in MAS to gather the state information and sent the control command back to each agent to reach a global goal. Due to the powerful nature of the central controller, control commands can be determined well and quickly. But when it fails, the whole system will be completely paralyzed. In contrast, decentralized control means that each agent has its own controller to collect and control the agent's own state information. Under this architecture, although the global goal cannot be achieved, the possibility of paralyzing the entire system due to the failure of the controller is avoided

Besides, the formation control is also a topic in MAS (cite:formation control). Its purpose is to keep a MAS in a formation while moving. Although formation control provides a simple framework for the control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible. Because there are many different sacles and types of tasks that must be handled in a disaster relief environment, agents in URTS need to organize multiple teams of different sacles and types to deal with. In this situation, it is more reasonable to treat each agent as an independent individual and design an independent trajectory for the agent to follow.

The external disturbances during tracking control must also be considered. The agent

The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control)
the control problem of robot
FTC
disturbance

@@

% \PARstart{W}{ith}

@@

\textbf{Notation 1:} 
% $diag(A_1, A_2, \dots, A_n)$: a block diagonal matrix with main diagonal blocks $A_1, A_2, \dots, A_n$.
$A^T$: transpose of A. $A > 0$: a positive definite matrix. $(a_n)$: sequence. $(a_{k_n})$: subsequence. $\vert{S}\vert$: size of a set $S$. $\otimes$: Kronecker product. $I_n$: n-dimension identity matrix. $x(t)\in L_2\begin{bmatrix}
    0,t_f 
\end{bmatrix}$ if $\int^{t_f}_{0}x^T(t)x(t)dt<\infty$. $Sym(A)$: sum of a matrix $A$ and its tranposed, i.e., $Sym(A) = A+A^T$.

\section{PRELIMINARIES OF search and rescue URTS}
The URTS will start with a given search and rescue area, and ends with searching task completed. The URTS is composed of $N_j$ teams and a ground station. Each team contains $1$ UAV and $N_i-1$ robots. Hence, the $i$th agent in the $j$th team is denoted as $agent_{i,j}$, where $i=1,2,...,N_i$ and $j=1,2,...,N_j$. The UAVs are chosed as the first agents in each team, i.e., $agent_{1,j}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

To complete search tasks, each team is designed to be responsible for a small area of the overall search area, and each agent will be assigned an appropriate path to cover the area. To complete rescue tasks, whenever a target (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of target. It can be expected that there has multiple search or rescue tasks need to be performed at the same time but there has multiple agents. If each agent can only perform one task at a time, then there exist many feasible way of task allocation. Usually we want this allocation to be optimal, which can be achieved by solving the dynamic task allocation problem.

If a task is to reach a location of certain goal, there must exist multiple feasible paths. Similar to task allocation, we usually want to find an optimal path. Besides, it's necessary to concern about collision between agents or between agents and obstacles in the actual scenario, so each agent will also sense distance-related information about its surrounding and send it back to the ground station. The ground station will combine this information with the goal assigned by task allocation algorithm and make a decision to avoid obstacles and other agents nearby. That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.

We need to design some behavior to follow the path found by path planning algorithm especially for agents with complex mechanical systems like robots. Since such a system has a high degree of freedom, there are many ways to follow the same path (e.g., a robot can walk or run to follow the same path). Furthermore, agents in a search and rescue system are not always following a trajectory. Sometimes they need the behavior such as stop to look around, get supplies and put supplies. To meet these needs, a behavioral layer is necessary. The behavior layer gives an appropriate behavior to fulfill an actual requirement. In order to make an behavior, we must design a corresponding motion which is handled by local motion planning. The motion is a desired reference trajectory for an actual mechanical system to follow. Finally, a tracking controller is designed to follow the desired reference trajectory.

To clarify this issue, a more detailed system architecture for each agent is needed. Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in search and rescue is proposed as shown in Fig. \ref{fig:sys}. The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents and an occupy map. The visual object recognition block provides distance information and object information through sensor info. The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot sees a obstacle and decides to climb through it). The detailed functions of remaining 5 blocks, i.e., Tack Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.

% To determine the behavior, agent needs the information about enviroment. The sensing data which include external enviroment information and internal system information is feedback to Behavior Layer to assist in judging the present state (fig:system).

@@

\subsection{Task Allocation}
In the URTS, it can be expected that each agent will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agent and task is more than one, and each agent has different capabilities (e.g. moving speed or load capacity) and status (e.g. their own position or the amount of supplies carried), and each task has different characteristics (e.g. Urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which makes us want to find the optimal allocation. This problem is refered as Task Allocation Problem or Multi-robot Task Allocation (MRTA) Problem. A problem formulation and problem modeling can be found in \cite{Khamis2015}. Although there are many different problem definitions and many problem models to solve this issue, the common goal is to find a set of task-agent pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned and therefore do not further discuss this issue. In other words, every agent knows a destinition it need to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real search and rescue system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}

\subsection{Path Planning}
After a target point is assigned for each agent, next step is to find a collision-free path from current position to it. There are several path planning algorithm to handle this problem, in this article, a roadmap-based path planning algorithm is used. This method attempts to discretize the search space into interconnected roads and find the path on it. According to the roadmap construction method, it can be divided into deterministic and sample-based. According to the way of pathfinding, it can be divided into multi-query planner and single-query planner \cite{elbanhawi2014sampling}. Multi-query planner divides pathfinding into learning phase in which a roadmap is bulit and query phase in which a graph search algorithm is used to find a best path within paths. Some representative planners are Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}. Relatively speaking, single-query planner completes pathfinding by constructing and querying at the same time, that is to say, the roadmap will be constructed incrementally and toward the goal. Some representative planners such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}. However, the environment is dynamic rather static for URTS so some extra structure need to impose on aforementioned planner. Some common dynamic planner also can be found in \cite{elbanhawi2014sampling}, such like PRM with D* search algorithm, dynamic RRT, and extended RRT.

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to Local Motion Planning to deal with. The reason is that URTS is a large-scale system, which makes the environment in which it is located changes more violently and will leads to many corresponding behaviors which path constraints will not necessarily be the same (e.g., curvature constraints of two behavior: running and walking are expected to be different for robot). In this case, Path Planning becomes a higher-level planner which regard agent as a point without kinodynamic constraints while the decision of the behavior and the corresponding motion will be handed over to the next two layers: Behavior Layer and Local Motion Planning.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

>>>>

\begin{document}
% \captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Fig.}}

\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

\title{Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage}
% \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
% \uppercase{Second B. Author\authorrefmark{2}, and Third C. Author,
% Jr}.\authorrefmark{3},
% \IEEEmembership{Member, IEEE}}
% \address[1]{National Institute of Standards and 
% Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
% \address[2]{Department of Physics, Colorado State University, Fort Collins, 
% CO 80523 USA (e-mail: author@lamar.colostate.edu)}
% \address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
% 80309 USA}
% \tfootnote{This paragraph of the first footnote will contain support 
% information, including sponsor and financial support acknowledgment. For 
% example, ``This work was supported in part by the U.S. Department of 
% Commerce under Grant BS123456.''}

@@

\begin{abstract}
In this study, we investigate a UAVs and biped robots team system (URTS) for search and rescue usage. The system architecture of URTS is proposed to illustrate the issues that need to be addressed in URTS and the relationships between them. Then we focus on two issues, local motion planning and tracking control. We discuss the methods of local motion planning for UAV flying behavior and robot walking behavior, and then give the control methods for UAV and robot. The relationship between the two issues, the transformation of the reference trajectory, is also explored in detail. By converting the dynamics model of UAV and robot into a unified agent model, a design method for a $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agent in URTS. A novel smoothing signal model of fault signal is embedded into the linearized system to active FTC through observer estimation. The design of this $H_\infty$ observer-based FTC is transformed into a linear matrix inequality (LMI) -constrained optimization problem by a two-step design procedure. Finally, with the help of MATLAB LMI Toolbox, the tracking problem of UAV and robot in URTS is effectively solved. Simulations are given ...
\end{abstract}

\begin{keywords}
biped robot, fault-tolerant control, heterogeneous multi-agent system, robust $H_\infty$ control, search and rescue, smoothing signal model, UAV, UAVs-UGVs team system
\end{keywords}

\titlepgskip=-15pt

\maketitle

\section{Introduction}
% unmanned vvehcile
\PARstart{I}{n} recent years, the unmanned vehicle (UV) has attracted attention due to the advances in communication technology, sensing devices, and computing power. It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans. Due to these benefits, it has been widely used in many scenarios, such as search and rescue, battlefield, logistics and transportation, and surveillance, etc (cite:UV). Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}. However, the cost is that the design of such a multi-agent system (MAS) becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, task allocation, and cooperation between agents. In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued (cite:HMAS). Compared with homogeneous multi-agent system, it can adapt to a wider variety of application scenarios because each agent has different aptitudes.

To construct an unmanned HMAS, the three required key capabilities are perception, decision-making and control. Perception is to obtain information through the sensor (e.g., localization or computer vision), decision-making is to make decisions through the sensor information, and control is to execute the decision-making content through the actuator. To limit the scope of this paper, we focus on decision-making and control only. The three main problem of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance. Task allocation is to optimally assign tasks to each agent, subject to constraints such as agent capabilities, fuel cost, time cost, etc \cite{9476736}. Path planning is to optimally plan paths to each agent, subject to constraints such as agent kinodynamic properties, distance, obstacles collision, etc (cite: path planning). Collision avoidance is to avoid collision with obstacles. Although collision avoidance is often concerned in path planning part, the collision avoidance system is also independently studied because of the requirements for the safety and reliability of the actual system \cite{9108245}.

Although there are many types of UVs to make up an unmanned HMAS, Unmanned Aerial Vehicle (UAV) and Unmanned Ground Vehicle (UGV) have been the subject of major recent research because of their availability and applicability (cite:UAV-UGV). Additionally, the complementarity between them also makes such a system more potential. In other words, UAV is widely used in reconnaissance due to the high mobility. However, the carrying capacity of UAV is very low compared to UGV since there is no ground support. In contrast, UGV has higher carrying capacity but is easily restricted by ground obstacles and cannot move at high speed. For these reasons, a hybrid UAVs-UGVs team system will be more appealing. To discuss more concretely, we consider an UAVs-UGVs team system for search and rescue. For the need for search mobility, we choose quadrotor aircraft as UAV. In order to deal with the complex terrain of the search and rescue environment, we choose biped robot as UGV. Even though other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system.

To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent search and rescue system, such as task allocation problem, path planning problem or control problem. Additionally, few literatures illustrate the relationship between these problems. This leads us to propose an system architecture of UAVs-robots team system (URTS) for search and rescue usage. The flowchart of decision-making and control process of URTS is also given. We divide it into five main hierarchical processes, i.e., tack allocation, path planning, behavior layer, local motion planning and tracking control. It is because the UTRS needs to be able to assign different tasks to agents to perform first. After a task is assigned, if the task is to reach a target location, a path to reach it needs to be planned. To make agent move on the path, a behavior corresponding to the environment is required to determine. Then, a local motion corresponding to the behavior of the agent needs to be planned. Finally, a controller must be designed to track the trajectory of the motion. In order to further limit the scope of the study, we will focus on the latter two processes. But to illustrate how the whole system works, the first three problems are also briefly stated.

% To discuss the local motion planning problem and tracking control problem, the real mechanical system for each agent corresponds must be considered. To meet the need for search mobility, we choose quadrotor aircraft as UAV. The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control). In order to deal with the complex terrain of the search and rescue environment, biped robot was chosen as the UGV. Although other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system. However, to let the biped robot moving, not only the control problem (cite: robot control) but also the local motion planning problem need to be solved. The local motion planning of the walking of biped robot, i.e., stable walking pattern generation, is discussed in this paper. Related researches can be found in (cite: walking pattern).

The local motion planning is the bridge between path planning and tracking control since the path found by path planning algorithm and the path enforced to follow by a controller are not necessarily the same. The reason is that path planning algorithm usually treats the agent as a point, while the actual agent in the physical world is a mechanical system for the tracking control design. A mechanical system means that there exist kinodynamic constraints. This makes certain paths impossible to follow for an actual agent, such as paths that are not smooth, have too large curvature, or require too large velocity and acceleration. Although there are some literatures directly tackle the kinodynamic constraints path planning problem \cite{9384209}, this paper splits path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity. Through this decomposition, we can focus on the local motion planning of specific behaviors. The motion planning of flying behavior for UAV and walking behavior for robot is studied in this paper, especially the latter. The local motion planning of walking of biped robot, i.e., stable walking pattern generation, is a popular research topic due to its challenge(cite: walking pattern).

The tracking control is to control an agent to follow a desired trajectory. There are many control strategy for MAS. According to the way of the design of controller, it can be divided into centralized control and decentralized control in control field \cite{8931370}. Centralized control means there exist a powerful central controller in MAS to gather the state information and sent the control command back to each agent to reach a global goal. Due to the powerful nature of the central controller, control commands can be determined well and quickly. But when it fails, the whole system will be completely paralyzed. In contrast, decentralized control means that each agent has its own controller to collect and control the agent's own state information. Under this architecture, although the global goal cannot be achieved, the possibility of paralyzing the entire system due to the failure of the controller is avoided.

Besides, the formation control is also a topic in MAS (cite:formation control). Its purpose is to keep a MAS in a formation while moving. Although formation control provides a simple framework for the control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible. It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment. In this situation, it is more reasonable to treat each agent as an independent individual and design an independent trajectory for the agent to follow.

The external disturbances during tracking control must also be considered. The agent ...
% The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
% the control problem of robot

Fault-tolerant contrl (FTC) ...

Based on the foregoing, a robust $H_\infty$ decentralized fault-tolerant tracking control strategy is proposed to deal with the control problem in URTS.

@@

@@

\textbf{Notation 1:} 
% $diag(A_1, A_2, \dots, A_n)$: a block diagonal matrix with main diagonal blocks $A_1, A_2, \dots, A_n$.
$A^T$: transpose of A. $A > 0$: a positive definite matrix. $(a_n)$: a sequence. $(a_{k_n})$: a subsequence of a sequence $(a_n)$. $[a_{j,k}]$: A matrix with the entries $a_{j,k}$ in the $j$th row and $k$th column. $\vert{S}\vert$: size of a set $S$. $\otimes$: Kronecker product. $I_n$: n-dimension identity matrix. $x(t)\in L_2\begin{bmatrix}
    0,t_f 
\end{bmatrix}$ if $\int^{t_f}_{0}x^T(t)x(t)dt<\infty$. $Sym(A)$: sum of a matrix $A$ and its tranposed, i.e., $Sym(A) = A+A^T$.

\section{PRELIMINARIES OF search and rescue URTS}
The URTS will start with a given search and rescue area, and end with mission completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $i$th agent in the $j$th team is denoted as $agent_{i,j}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$. The UAVs are chosed as the first agents in each team, i.e., $agent_{1,j}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

To complete search tasks, each team is designed to be responsible for a small area of the overall search area, and each agent will be assigned an appropriate path to cover the area. To complete rescue tasks, whenever a target (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of target. 
% It can be expected that there has multiple search or rescue tasks need to be performed at the same time but there has multiple agents. If each agent can only perform one task at a time, then there exist many feasible way of task allocation. Usually we want this allocation to be optimal, which can be achieved by solving the dynamic task allocation problem.

If a task is to reach a location of certain goal, we need to find a collision-free path to reach it. 
% there must exist multiple feasible paths. Similar to task allocation, we usually want to find an optimal path. 
% Besides, it's necessary to concern about collision between agents or between agents and obstacles in the actual scenario, 
Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station. The ground station will combine this information with the goal location assigned by task allocation algorithm and make a decision to avoid obstacles and other agents nearby.
% That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.

We need to determine specific behavior to follow the path found by path planning algorithm according to the situation of the environment especially for agents with complex mechanical systems like robots. Since such a system has a high degree of freedom, there are many ways to follow the same path (e.g., a robot can walk or run to follow the same path). Furthermore, agents in URTS are not always following the path. Sometimes they need the behavior such as stop to look around, get supplies and put supplies. To meet these needs, a behavioral layer is necessary.
% The behavior layer decides an appropriate behavior based on the circumstances.

In order to make an behavior, we must design a corresponding motion which is handled by local motion planning. The motion is a desired reference trajectory for an actual mechanical system to follow. Finally, a tracking controller is designed to follow this desired reference trajectory.

The agents overall have the same system architecture in URTS except for some subprocess differences. Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in search and rescue is proposed as shown in Fig. \ref{fig:sys}. The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents $q_{start}$ and an occupy map $\mathcal{C}$. The visual object recognition block provides distance information and object information through the analysis of sensor information. The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot sees a obstacle and decides to climb through it). The detailed functions of remaining 5 blocks, i.e., Tack Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.

% To determine the behavior, agent needs the information about environment. The sensing data which include external environment information and internal system information is feedback to Behavior Layer to assist in judging the present state (fig:system).

@@

\subsection{Task Allocation}
In the URTS, it can be expected that each agent will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g. moving speed or load capacity) and status (e.g. their own position or the amount of supplies carried), and each task has different characteristics (e.g. Urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which makes us want to find the optimal allocation. This problem is refered as task allocation problem or multi-robot task allocation problem. A problem formulation and problem modeling can be found in \cite{Khamis2015}. Although there are many different problem definitions and many problem models to solve this issue, the common goal is to find a set of task-agent pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned and therefore do not further discuss this issue. In other words, every agent knows a destinition $q_{goal}$ it need to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real search and rescue system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}

\subsection{Path Planning}
After a target point is assigned for each agent, next step is to find a collision-free path from current position to it. There must exist multiple feasible paths to go. Similar to task allocation, we usually want to find an optimal path. There are several path planning algorithm to handle this problem. Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper uses it as the path planning method of UTRS. This method attempts to discretize the search space into interconnected roads and find the path on it. 
% According to the roadmap construction method, it can be divided into deterministic and sample-based.

According to the way of pathfinding, it can be divided into multi-query planner and single-query planner \cite{elbanhawi2014sampling}. Multi-query planner will first construct a roadmap and then use the graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}. Single-query planner will complete pathfinding by constructing and querying simultaneously,
%  i.e., the roadmap will be constructed incrementally and toward the goal, 
such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}. However, the environment is dynamic rather static for URTS so some extra structure need to impose on aforementioned planner. Some common dynamic planner can also be found in \cite{elbanhawi2014sampling}, such like PRM with D* search algorithm, dynamic RRT, and extended RRT. All of the above common roadmap-based planners can be applied to the URTS.

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to Local Motion Planning block to deal with. The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and the constraints on these behaviors will vary. (e.g., curvature constraints of two behavior: running and walking are expected to be different for robot). In this case, a unified planner will become overly complex and impracticable. For this reason, we divide path planning into three subprocess, i.e., Path Planning, Behavior Layer and Local Motion Planning. Then, the global planner, Path Planning block, will regard agent as a point without kinodynamic constraints. The local planners, Local Motion Planning block, will consider the motion planning of a specific behavior.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or sayed waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space $\mathcal{C}$. Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques. Goal configuration is obtained by previous block, Task Allocation. Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline. $\mathcal{C}$ is a space contain all possible configuration of agent which composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$. For a simpler explanation of how the URTS works, the following assumption is made.
\begin{assumption}
    The locating ability of the URTS is perfect so every agent can know its current configuration $q_{start}$.
\end{assumption}
\begin{assumption}
    A Task Allocation algorithm is already designed so that every agent can know its goal configuration $q_{goal}$.
\end{assumption}
\begin{assumption}
    The URTS is supposed to have an perfect real-time mapping ability so a real-time configuration space $\mathcal{C}$ can be obtain.
\end{assumption}
\begin{assumption} \label{asm:collision} % UAV do not consider obstacle collisions a little wierd.
    UAVs do not consider obstacle collisions because there are few obstacles in the air. Hence, the path of UAVs can be directly assigned rather found by planner. Robots do not consider obstacle collisions in the direction perpendicular to the ground. 
\end{assumption}
From above assumptions, a path of agent can be expressed as a sequence
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be a goal changing that made by human or Task Allocation. For robot, it can be a collision detecting by a dynamic roadmap-based planner. The results path $(\sigma_n)$ is passed to next block, Behavior Layer.

\subsection{Behavior Layer}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
Path Planning tells agents where to go but not how. Take robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ in real scenario. These behaviors with changing position are called "moving" in this paper. Besides, the agents do not always moving. Somtimes they has to suspend to take a action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls). These behaviors without changing position are called an "action" in this paper. More behaviors can be added so that the agent can have more way to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
It is to say that the path $(\sigma_n)$ is divided into many segments and each corresponding to a specific behavior. Judging an appropriate behavior according to the current environment will be a rather complicated project, so this article only gives the structure of the behavior set. The set of behavior $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig. \ref{fig:behavior}.
